A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-20 sections/appendix/descrete_event_simulation/main.tex
Add subsections in How-to

The package can be installed by either running:

@@

in the command line or via the instructions provided in the GitHub repository.
% TODO: Cite repository
The required arguments that need to be passed to the simulate\_model() function
are the following:
\begin{itemize}
    \item lambda\_1 (\(\lambda_1\)): The arrival rate of class 1 individuals.
    \item lambda\_2 (\(\lambda_2\)): The arrival rate of class 2 individuals.
    \item mu (\(\mu\)): The service rate of the servers.
    \item num\_of\_servers (\(C\)): The number of servers in the system.
    \item threshold (\(T\)): The threshold that indicates when to start blocking 
    class 2 individuals.
\end{itemize}

@@

Additional arguments that can be passed to the function are:
\begin{itemize}
    \item \textit{system\_capacity}: The maximum number of individuals in 
    waiting zone 2.
    \item \textit{buffer\_capacity}: The maximum number of individuals in 
    waiting zone 1.
    \item \textit{seed\_num}: The seed number for the random number generator.
    \item \textit{runtime}: How long to run the simulation for.
\end{itemize}

From a single run of the simulation the data records can be used to get the
average for certain performance measures. 
The following code can be used to get the mean waiting time, blocking time, 
service time and the proportion of individuals within target.

@@

To reduce the effects of stochasticity in the simulation, the simulation can be run
numerous times and get the average performance measures out of all the runs.

@@

@@

>>>>

\subsubsection{How to install:}
The package can be installed by either running:

@@

in the command line or via the instructions provided in the GitHub repository.
% TODO: Cite repository

\subsubsection{How to simulate the model:}
The required arguments that need to be passed to the 
\lstinline[style=pystyle]{simulate_model()} function
are the following:
\begin{itemize}
    \item lambda\_1 (\(\lambda_1\)): The arrival rate of class 1 individuals.
    \item lambda\_2 (\(\lambda_2\)): The arrival rate of class 2 individuals.
    \item mu (\(\mu\)): The service rate of the servers.
    \item num\_of\_servers (\(C\)): The number of servers in the system.
    \item threshold (\(T\)): The threshold that indicates when to start blocking 
    class 2 individuals.
\end{itemize}

@@

Additional arguments that can be passed to the function are:
\begin{itemize}
    \item \textit{system\_capacity} (\(N\)): The maximum number of individuals in 
    waiting zone 2.
    \item \textit{buffer\_capacity} \(M\): The maximum number of individuals in 
    waiting zone 1.
    \item \textit{seed\_num}: The seed number for the random number generator.
    \item \textit{runtime}: How long to run the simulation for.
\end{itemize}

\subsubsection{How to get the performance measures for a single run:}
From a single run of the simulation the data records can be used to get the
average for certain performance measures. 
The following code can be used to get the mean waiting time, blocking time, 
service time and the proportion of individuals within target.

@@

\subsubsection{How to get the average performance measures:}
To reduce the effects of stochasticity in the simulation, the simulation can be 
run numerous times and get the average performance measures out of all the runs.

@@

\subsubsection{How to get the steady state probabilities vector \( \pi \):}

@@

\subsubsection{How to get the optimal distribution of class 2 individuals among 2 
queuing models:}
